Biologically-Constrained Region Merging for Connectome Reconstruction

### 2018-03-14 papers/eccv2018/0_introduction.tex
minor edits to first few sections, removed all red Xs

The field of connectomics considers the problem of reconstructing the wiring diagram of the brain at nanometer resolutions to enable new insights into the workings of the brain~\cite{haehn2017scalable,kasthuri2015saturated}. 
%Recent advancements in image acquisition using multi-beam serial-section electron microscopy (sSEM) allow researchers to produce terabytes of image data per hour~\cite{hildebrand2017whole}. 
%It is infeasible for domain experts to manually reconstruct this vast amount of image data~\cite{haehn2014design}. 
State-of-the-art automatic 3D reconstruction approaches use pixel-based convolutional neural networks (CNNs) and watershed transforms to generate initial over-segmentation, followed by region merging steps~\cite{seymour2016rhoananet,lee2015recursive,nunez2014graph,parag2017anisotropic,ronneberger2015u,zlateski2015image}.
For region merging, most methods do not use prior biological knowledge of the 3D shape of neural structures.
Simple threshold-based mean agglomeration methods can achieve superhuman resolution  small-sized volumes~\cite{lee2017superhuman}.

@@

@@

%Our approach operates at a level of abstraction above existing pixel-based methods. 
%This allows us to leverage both local and global information to produce more accurate reconstructions. 
With the biological constraints, we can make use of both geometric and topological prior information to produce more accurate reconstructions (Fig.~\ref{fig:teaser_pipeline}).
Our method is independent of image resolution and acquisition parameters, enabling its application to isotropic and anisotropic image data without retraining.
Images generated by electron microscopes often differ in appearance because of variations in staining techniques \cite{briggman2012volume}.
By removing the dependence of our algorithm on the input images, we greatly reduce the need for additional costly ground truth data for each new stack of images.
Using the graph induced by the segmentation allows us to enforce global biological constraints on the reconstruction. 
Our dual approach of assessing local decisions in a global context yields accuracy improvements over existing reconstruction methods.

This work makes three contributions:
first, a novel top-down framework that extracts graphs from skeletonized 3D segmentations for improved region merging for neural reconstruction of connectomics data; 
next, a region-based CNN classifier to detect split errors; 
%(3) an empirical evaluation of our method on several connectomics datasets;  % this is not contribution
last, improved performance over a state-of-the-art pixel-based reconstruction approach on average by $8.2\%$ while maintaining scalable runtimes for large volumes.

>>>>

The field of connectomics considers the problem of reconstructing the wiring diagram of the brain at nanometer resolutions to enable new insights into the workings of the brain~\cite{haehn2017scalable,kasthuri2015saturated}. 
%Recent advancements in image acquisition using multi-beam serial-section electron microscopy (sSEM) allow researchers to produce terabytes of image data per hour~\cite{hildebrand2017whole}. 
%It is infeasible for domain experts to manually reconstruct this vast amount of image data~\cite{haehn2014design}. 
State-of-the-art automatic 3D reconstruction approaches use pixel-based convolutional neural networks (CNNs) and watershed transforms to generate initial over-segmentation, followed by region merging steps~\cite{seymour2016rhoananet,lee2015recursive,nunez2014graph,parag2017anisotropic,ronneberger2015u,zlateski2015image}.
For region merging, most methods do not use prior biological knowledge of the 3D shape of neural structures.

@@

We can make use of both geometric and topological prior information to produce more accurate reconstructions matching the underlying biology (Fig.~\ref{fig:teaser_pipeline}).

@@

%Our approach operates at a level of abstraction above existing pixel-based methods. 
%This allows us to leverage both local and global information to produce more accurate reconstructions.

Our method is independent of image resolution and acquisition parameters, enabling its application to isotropic and anisotropic image data without retraining.
Images generated by electron microscopes often differ in appearance because of variations in staining techniques \cite{briggman2012volume}.
By removing the dependence of our algorithm on the input images, we greatly reduce the need for additional costly ground truth data for each new stack of images.
Using the graph induced by the segmentation allows us to enforce global biological constraints on the reconstruction. 
Our dual approach of assessing local decisions in a global context yields accuracy improvements over existing reconstruction methods.

This work makes three contributions:
first, a novel top-down framework that extracts graphs from skeletonized 3D segmentations for improved region merging for neural reconstruction of connectomics data; 
next, a region-based CNN classifier to detect split errors; 
%(3) an empirical evaluation of our method on several connectomics datasets;  % this is not contribution
last, improved variation of information performance over a state-of-the-art pixel-based reconstruction approach on average by $8.2\%$ while maintaining scalable runtimes for large volumes.

### 2018-03-14 papers/eccv2018/2_method.tex
minor edits to first few sections, removed all red Xs

Our method is illustrated in Fig.~\ref{fig:teaser_pipeline}.
From the input segmentation we generate a graph $G$ with nodes $N$ and edges $E$ with weights $w_e$. 
The nodes correspond to labeled segments from the input data with edges between merge candidates.
We propose the following three steps to formulate and then partition the graph while obeying constraints from the underlying biology.
First, we only consider merging segments based on a skeletonized representation of the input segmentation (Fig.~\ref{fig:teaser_pipeline}a).
This is enables us to reduce the number of nodes in the graph based on prior knowledge of the shape of neuronal processes.
Second, we train a convolutional neural network that learns biological constraints based on the shapes of the input segmentation (Fig.~\ref{fig:teaser_pipeline}b).
This network generates probabilities that segments belong to the same neuron based only on the segmentations. 
An example of one such learned constraint is that neurons have small turning radii (Fig.~\ref{fig:turn-radii}).
Third, we partition the graph using a lifted multicut formulation with additional acyclic constraints to enforce global biological constraints (Fig.~\ref{fig:teaser_pipeline}c).
The lifted multicut solution is globally consistent which we then augment to produce a tree-structured graph (i.e., one with no cycles).

\subsection{Skeleton-Based Graph Generation}
%\subsubsection{Node Generation}
\label{sec:skeletonization}
Most region merging methods create the region graph by removing small-sized segments and linking each pair of adjacent segments, which can still lead to a large graph size due to the irregular shape of neural structures.
We here use the skeleton representation of the segmentation and reduce the graph size with the geometric constraints on the connectivity of two adjacent segments to prune edges.
% a bit trivial, as everyone is doing this. maybe no need to mention
% \subsubsection{Node Pruning}
% %The simplest node generation strategy creates one node for every unique segment label in the input volume. 
% Some labels in the volume correspond to very small structures that are likely the result of segmentation errors, typically in regions with noisy raw image data. 
% It is difficult to extract useful shape features from these segments because of their small, often random, shape. 
% We prune these nodes from the graph by removing all segments with fewer than a empirical threshold $t_{seg} = 20,000$ voxels. 
% This removes on average \TODO{XX}\% of the segments in our  datasets (Sec.~\ref{sec:dataset}), leaving us with around $\TODO{XX}$ nodes per dataset (\TODO{X nodes per micrometer}). 
% Despite the large number of segments, these regions only take up \TODO{XX}\% of the total volume on average.

@@

For the input of the network, we extract a cubic region of interest (ROI) around each endpoint $e$ in $\mathbb{S}_c$ as input to the CNN. 
The CNN receives three input channels for every voxel in the ROI around segments $l_1$ and $l_2$. 
The input in all of the channels is in the range $\{-0.5, 0.5\}$. 
The first channel is $0.5$ only if the corresponding voxel has label $l_1$. 
The second channel is $0.5$ only if the corresponding voxel has label $l_2$. 
The third channel is $0.5$ if the corresponding voxel is either $l_1$ or $l_2$.
We do not use the raw EM image information to avoid the need to retrain the network on datasets that have been stained differently or imaged at different resolution. 
This reduces the need for generating costly manually-labeled ground truth.

@@

\begin{figure}[t]
	\centering
	\begin{minipage}{0.32\linewidth}
		\includegraphics[width=\linewidth]{./figures/split_error1.png}		
	\end{minipage}
	\hfill
	\begin{minipage}{0.32\linewidth}
		\includegraphics[width=\linewidth]{./figures/split_error2.png}				
	\end{minipage}
	\hfill
	\begin{minipage}{0.32\linewidth}
		\includegraphics[width=\linewidth]{./figures/split_error3.png}
	\end{minipage}
	\caption{Three erroneously split segments.}
	\label{fig:merge_candidates}
\end{figure}
\subsection{Optimization-Based Graph Partition}

After graph construction, we segment the graph in a globally consistent manner while enforcing topological constraints on the output.
\\~\\
%\subsubsection{Lifted Multicut}
\noindent\textbf{Lifted Multicut}
After constructing the graph we seek to partition it into labels where every label corresponds to a neuronal process. 
We formulate this graph partitioning problem as a multicut problem.
There are two primary benefits to using a multicut formulation. 
First, the number of segments in the final graph is not predetermined but depends on the input. 
Second, this minimization produces globally consistent solutions (i.e., a boundary remains only if the two corresponding nodes belong to unique segments)~\cite{keuper2015efficient}.

We apply the algorithms of Keuper et al.~\cite{keuper2015efficient} to produce a feasible solution to the multicut problem using greedy additive edge contraction.
Following their example, we employ the generalized lifted multicut formulation.
Traditional multicut solutions only consider the probabilities that two adjacent nodes belong to the same segment. 
In the lifted extension to the problem, we can penalize non-adjacent nodes that belong to different segments. 
These penalties between non-adjacent nodes are called lifted edges. 
Ideally these lifted weights represent the probability that two nodes belong to the same neuron.
However, determining such probabilities is computationally expensive.
We approximate these probabilities by finding the maximal probable path between any two nodes using Dijkstra's algorithm~\cite{keuper2015efficient}.
This is an underestimate of the probability that two nodes belong to the same neuron since it does not consider all possible paths.
Since our graphs are sufficiently small, we can generate lifted edges between all pairs of nodes. 
\\~\\
\noindent\textbf{Edge Weight} 
We need to convert the probabilities into the following weighting scheme to solve the multicut problem with this heuristic~\cite{keuper2015efficient,andres2011probabilistic}.
Given the probability that the nodes belong to the same neuron is $p_e$, the edge weight $w_e$ is defined as
%p_e &=\mbox{CNN}(x_1, x_2) \\
\begin{align}
w_e = \log{\frac{p_e}{1 - p_e}} + \log{\frac{1 - \beta}{\beta}},
\end{align}
where $\beta$ is a tunable parameter that encourages over- or under-segmentation. 
\\~\\
%\subsubsection{Topological Constraints}
\noindent\textbf{Topological Constraints}
By reformulating the segmentation problem as a graph partitioning one, we can enforce some global constraints on our result based on the underlying biology.
Traditional hierarchical clustering algorithms do not rely on such constraints but consider local decisions independently.
We enforce a global constraint that neurons are tree-structured and should not contain cycles. 
The multicut problems returns a series of ``collapsed'' edges between nodes that belong to the same neuron.
We iterate over these edges in order of the probability of merge generated by our CNN. 
We ``collapse'' an edge only if it does not create a cycle in the graph.

>>>>

Our method is illustrated in Fig.~\ref{fig:teaser_pipeline}.
From the input segmentation we generate a graph $G$ with nodes $N$ and edges $E$ with weights $w_e$. 
The nodes correspond to labeled segments from the input data with edges between merge candidates.
We propose the following three steps to formulate and then partition the graph while obeying constraints from the underlying biology.
First, we only consider merging segments based on a skeletonized representation of the input segmentation (Fig.~\ref{fig:teaser_pipeline}a).
This enables us to reduce the number of nodes in the graph based on prior knowledge on the shape of neuronal processes.
Second, we train a convolutional neural network that learns biological constraints based on the shapes of the input segmentation (Fig.~\ref{fig:teaser_pipeline}b).
This network generates probabilities that segments belong to the same neuron based only on the segmentations. 
An example of one such learned constraint is that neurons have small turning radii (Fig.~\ref{fig:turn-radii}).
Third, we partition the graph using a lifted multicut formulation with additional acyclic constraints to enforce global biological constraints (Fig.~\ref{fig:teaser_pipeline}c).
The lifted multicut solution is globally consistent which we then augment to produce a tree-structured graph (i.e., one with no cycles).

\subsection{Skeleton-Based Graph Generation}
%\subsubsection{Node Generation}
\label{sec:skeletonization}
Most region merging methods create a region graph by removing small-sized segments and linking each pair of adjacent segments, which can still lead to a large graph size due to the irregular shape of neural structures.
We use a skeleton representation of the segmentation to reduce the graph size with the geometric constraints on the connectivity of two adjacent segments to prune edges.
% a bit trivial, as everyone is doing this. maybe no need to mention
% \subsubsection{Node Pruning}
% %The simplest node generation strategy creates one node for every unique segment label in the input volume. 
% Some labels in the volume correspond to very small structures that are likely the result of segmentation errors, typically in regions with noisy raw image data. 
% It is difficult to extract useful shape features from these segments because of their small, often random, shape. 
% We prune these nodes from the graph by removing all segments with fewer than a empirical threshold $t_{seg} = 20,000$ voxels. 
% This removes on average \TODO{XX}\% of the segments in our  datasets (Sec.~\ref{sec:dataset}), leaving us with around $\TODO{XX}$ nodes per dataset (\TODO{X nodes per micrometer}). 
% Despite the large number of segments, these regions only take up \TODO{XX}\% of the total volume on average.

@@

For the input of the network, we extract a cubic region of interest (ROI) around each endpoint $e$ in $\mathbb{S}_c$ as input to the CNN. 
The CNN receives three input channels for every voxel in the ROI around segments $l_1$ and $l_2$. 
The input in all of the channels is in the set $\{-0.5, 0.5\}$. 
The first channel is $0.5$ only if the corresponding voxel has label $l_1$. 
The second channel is $0.5$ only if the corresponding voxel has label $l_2$. 
The third channel is $0.5$ if the corresponding voxel is either $l_1$ or $l_2$.
We do not use the raw EM image information to avoid the need to retrain the network on datasets that have been stained differently or imaged at different resolution. 
This reduces the need for generating costly manually-labeled ground truth.

@@

\begin{figure}[t]
	\centering
	\begin{minipage}{0.32\linewidth}
		\includegraphics[width=\linewidth]{./figures/split_error1.png}		
	\end{minipage}
	\hfill
	\begin{minipage}{0.32\linewidth}
		\includegraphics[width=\linewidth]{./figures/split_error2.png}				
	\end{minipage}
	\hfill
	\begin{minipage}{0.32\linewidth}
		\includegraphics[width=\linewidth]{./figures/split_error3.png}
	\end{minipage}
	\caption{Three erroneously split segments.}
	\label{fig:merge_candidates}
\end{figure}
\subsection{Optimization-Based Graph Partition}
\label{sec:optimization}
After graph construction, we segment the graph in a globally consistent manner while enforcing topological constraints on the output.
\\~\\
%\subsubsection{Lifted Multicut}
\noindent\textbf{Lifted Multicut}
After constructing the graph we seek to partition it into labels where every label corresponds to a neuronal process. 
We formulate this graph partitioning problem as a multicut problem.
There are two primary benefits to using a multicut formulation. 
First, the number of segments in the final graph is not predetermined but depends on the input. 
Second, this minimization produces globally consistent solutions (i.e., a boundary remains only if the two corresponding nodes belong to unique segments)~\cite{keuper2015efficient}.

We apply the algorithms of Keuper et al.~\cite{keuper2015efficient} to produce a feasible solution to the multicut problem using greedy additive edge contraction.
Following their example, we employ the generalized lifted multicut formulation.
Traditional multicut solutions only consider the probabilities that two adjacent nodes belong to the same segment. 
In the lifted extension to the problem, we can penalize non-adjacent nodes that belong to different segments. 
These penalties between non-adjacent nodes are called lifted edges. 
Ideally these lifted weights represent the probability that two nodes belong to the same neuron.
However, determining such probabilities is computationally expensive.
We approximate these probabilities by finding the maximal probable path between any two nodes using Dijkstra's algorithm~\cite{keuper2015efficient}.
This is an underestimate of the probability that two nodes belong to the same neuron since it does not consider all possible paths.
Since our graphs are sufficiently small, we can generate lifted edges between all pairs of nodes. 
\\~\\
\noindent\textbf{Edge Weight} 
We need to convert the probabilities into the following weighting scheme to solve the multicut problem with this heuristic~\cite{keuper2015efficient,andres2011probabilistic}.
Given the probability that the nodes belong to the same neuron is $p_e$, the edge weight $w_e$ is defined as
%p_e &=\mbox{CNN}(x_1, x_2) \\
\begin{align}
w_e = \log{\frac{p_e}{1 - p_e}} + \log{\frac{1 - \beta}{\beta}},
\end{align}
where $\beta$ is a tunable parameter that encourages over- or under-segmentation. 
Since, there are many more lifted edges than adjacent edges, we scale down the lifted weights proportionally to their total number.  
~\cite{beier2017multicut}.
\\~\\
%\subsubsection{Topological Constraints}
\noindent\textbf{Topological Constraints}
By reformulating the segmentation problem as a graph partitioning one, we can enforce some global constraints on our result based on the underlying biology.
Traditional hierarchical clustering algorithms do not rely on such constraints but consider local decisions independently.
We enforce a global constraint that neurons are tree-structured and should not contain cycles. 
The multicut problems returns a series of ``collapsed'' edges between nodes that belong to the same neuron.
We iterate over these edges in order of the probability of merge generated by our CNN. 
We ``collapse'' an edge only if it does not create a cycle in the graph.

### 2018-03-14 papers/eccv2018/3_evaluation.tex
updated red Xs
minor edits to first few sections, removed all red Xs

\subsection{Method Configuration}
\noindent\textbf{Initial Segmentation}
%\label{sec:neuroproof}
%The segmentation of the Kasthuri dataset was computed by agglomerating 3D supervoxels produced by the watershed algorithm from 3D affinity predictions~\cite{zlateski2015image}. 
%A recent study by Funke et al.~\cite{funke2017deep} demonstrated superior performance of such methods over existing ones on anisotropic data. 
%We learn 3D affinities using MALIS loss with a U-net~\cite{ronneberger2015u,Turaga:2009}. 
%We apply the z-watershed algorithm with suitable parameters to compute a 3D oversegmentation of the volume. 
%The resulting 3D oversegmentation is then agglomerated using the technique of context-aware delayed agglomeration to generate the final segmentation~\cite{10.1371/journal.pone.0125825}.
For the Kasthuri dataset, we used the segmentation pipeline from Funke et al.~\cite{funke2017deep}. 
We first train a 3D affinity prediction U-Net model~\cite{ronneberger2015u} with MALIS loss~\cite{Turaga:2009} and apply the watershed and agglomeration method~\cite{funke2017deep} to obtain the final segmentation result.
For the FlyEM data, based on the authors' suggestion~\cite{takemura2017connectome}, we apply a context-aware delayed agglomeration algorithm~\cite{10.1371/journal.pone.0125825} that shows improved performance on this dataset over the pipeline used in the original publication. 
This segmentation framework learns voxel and supervoxel classifiers with an emphasis to minimize under-segmentation error. 
The algorithm first computes multi-channel 3-D predictions for membranes, cell interiors, and mitochondria, among other cell features. 
The membrane prediction channel is used to produce an over-segmented volume using 3D watershed, which is then agglomerated hierarchically up to a certain confidence threshold. 
We used exactly the same parameters as the publicly available code for this algorithm.
%For the Fib-25 challenge dataset, we use the segmentation from Funke et al. as our input~\cite{funke2017deep}.
\\~\\
\noindent\textbf{Graph Generation}
The two parameters for the graph pruning algorithm (Sec.~\ref{sec:skeletonization}) are $t_{low}$ and $t_{high}$. 
Ideally, our graph will have an edge for every over-segmented pair of labels with few edges between correctly segmented pairs. 
After considering various thresholds, we find that $t_{low} = \SI{210}{\nano\meter}$ and $t_{high} = \SI{300}{\nano\meter}$ produce expressive graphs with a scalable number of nodes and edges.
We explore these thresholds in greater detail in the supplemental material.
During implementation, we use nanometers instead of voxels for these thresholds to have uniform units across all datasets.
% Connectomics datasets often have lower sample resolutions in $z$ because of limitations during sample preparation. 
% Using nanometers allows us to have uniform units across all of these datasets and calculate the thresholds in voxels at runtime.
% Although the voxels vary between different datasets, the physical space remains constant. 
\\~\\
\noindent\textbf{Edge Weight Learning}
\label{sec:network-parameters}
We use half of the Kasthuri dataset for training and validation. 
We train on 80\% of the potential merge candidates for this volume.
We validate the CNN classifier on the remaining 20\% of the candidates. 
Since our input does not require the image data, we can train on the anisotropic Kasthuri data and test on the isotropic FlyEM data.

@@

%\noindent\textbf{Training Augmentation.}
Since our input is an existing segmentation of the EM images, there are very few training examples compared to per-pixel classifiers that can train on a unique window for each voxel. 
The Kasthuri dataset represents a region of brain over $\SI[product-units=single]{800}{\micro\meter}^3$ in volume and only yields 640 positive merge examples and 4821 negative ones.
To avoid overfitting our deep networks, we apply the following augmentations on the training examples.
During a single batch, we randomly select ten positive and negative examples. 
With probability 0.5, the example is reflected across the $xy$-plane. 
We then rotate the example by a random angle between $0$ and $360$ degrees using nearest neighbor interpolation. 
The supplemental material contains experiments demonstrating the benefits of this augmentation strategy.
We have 20,000 such examples per epoch.
\\~\\
\noindent\textbf{Graph Partition}
%We assign the edges in our graph a weight $w_e = \log{\frac{p_e}{1 - p_e}} + \log{\frac{1 - \beta}{\beta}}$ where $\beta$ is a tunable parameter. 
%Higher values of $\beta$ encourage over-segmentation.
Figure~\ref{fig:variation-of-information} shows our results for variables $\beta \in [0.5, 0.9]$. 
For our multicut analysis we use $\beta = 0.5$. There are many more lifted edges than adjacent edges. 
To prevent the lifted weights from dominating the objective function we weight each set of edges~\cite{beier2017multicut}.

\subsection{Error Metrics}
\label{sec:variation-of-information}
We evaluate the performance of the different methods using the split variation of information (VI)~\cite{meila2003comparing}.
Given a ground truth labeling $GT$ and our automatically reconstructed segmentation $SG$, over- and under-segmentation are quantified by the conditional entropies $H(GT | SG)$ and $H(SG | GT)$, respectively. 
Since we are measuring the entropy between two clusterings, lower VI scores are better.

>>>>

\subsection{Method Configuration}
\noindent\textbf{Initial Segmentation}
%\label{sec:neuroproof}
%The segmentation of the Kasthuri dataset was computed by agglomerating 3D supervoxels produced by the watershed algorithm from 3D affinity predictions~\cite{zlateski2015image}. 
%A recent study by Funke et al.~\cite{funke2017deep} demonstrated superior performance of such methods over existing ones on anisotropic data. 
%We learn 3D affinities using MALIS loss with a U-net~\cite{ronneberger2015u,Turaga:2009}. 
%We apply the z-watershed algorithm with suitable parameters to compute a 3D oversegmentation of the volume. 
%The resulting 3D oversegmentation is then agglomerated using the technique of context-aware delayed agglomeration to generate the final segmentation~\cite{10.1371/journal.pone.0125825}.
The segmentation of the Kasthuri dataset was computed by agglomerating 3D supervoxels produced by the z-watershed algorithm from 3D affinity predictions~\cite{zlateski2015image}. 
A recent study by Funke et al.~\cite{funke2017deep} demonstrated superior performance of such methods over existing ones on anisotropic data. 
We learn 3D affinities using MALIS loss with a U-net~\cite{ronneberger2015u,Turaga:2009}. 
We apply the z-watershed algorithm with suitable parameters to compute a 3D over-segmentation of the volume. 
The resulting 3D over-segmentation is then agglomerated using the technique of context-aware delayed agglomeration to generate the final segmentation~\cite{10.1371/journal.pone.0125825}.
For the FlyEM data, based on the authors' suggestion~\cite{takemura2017connectome}, we apply a context-aware delayed agglomeration algorithm~\cite{10.1371/journal.pone.0125825} that shows improved performance on this dataset over the pipeline used in the original publication. 
This segmentation framework learns voxel and supervoxel classifiers with an emphasis to minimize under-segmentation error. 
The algorithm first computes multi-channel 3-D predictions for membranes, cell interiors, and mitochondria, among other cell features. 
The membrane prediction channel is used to produce an over-segmented volume using 3D watershed, which is then agglomerated hierarchically up to a certain confidence threshold. 
We used exactly the same parameters as the publicly available code for this algorithm.
%For the Fib-25 challenge dataset, we use the segmentation from Funke et al. as our input~\cite{funke2017deep}.
\\~\\
\noindent\textbf{Graph Generation}
The two parameters for the graph pruning algorithm (Sec.~\ref{sec:skeletonization}) are $t_{low}$ and $t_{high}$. 
Ideally, our graph will have an edge for every over-segmented pair of labels with few edges between correctly segmented pairs. 
After considering various thresholds, we find that $t_{low} = \SI{210}{\nano\meter}$ and $t_{high} = \SI{300}{\nano\meter}$ produce expressive graphs with a scalable number of nodes and edges.
We explore these thresholds in greater detail in the supplemental material.
During implementation, we use nanometers instead of voxels for these thresholds to have uniform units across all datasets.
% Connectomics datasets often have lower sample resolutions in $z$ because of limitations during sample preparation. 
% Using nanometers allows us to have uniform units across all of these datasets and calculate the thresholds in voxels at runtime.
% Although the voxels vary between different datasets, the physical space remains constant. 
\\~\\
\noindent\textbf{Edge Weight Learning}
\label{sec:network-parameters}
We use half of the Kasthuri dataset for training and validation. 
We train on 80\% of the potential merge candidates for this volume.
We validate the CNN classifier on the remaining 20\% of the candidates. 
Since our input does not require the image data, we can train on the anisotropic Kasthuri data and test on the isotropic FlyEM data.

@@

%\noindent\textbf{Training Augmentation.}
Since our input is an existing segmentation of the EM images, there are very few training examples compared to per-pixel classifiers that can train on a unique window for each voxel. 
The Kasthuri dataset represents a region of brain over $\SI[product-units=single]{800}{\micro\meter}^3$ in volume and only yields 640 positive merge examples and 4821 negative ones.
To avoid overfitting our deep networks, we apply the following augmentations on the training examples.
During a single batch, we randomly select ten positive and negative examples. 
With probability 0.5, the example is reflected across the $xy$-plane. 
We then rotate the example by a random angle between $0$ and $360$ degrees using nearest neighbor interpolation. 
The supplemental material contains experiments demonstrating the benefits of this augmentation strategy.
We have 20,000 such examples per epoch.
\\~\\
\noindent\textbf{Graph Partition}
%We assign the edges in our graph a weight $w_e = \log{\frac{p_e}{1 - p_e}} + \log{\frac{1 - \beta}{\beta}}$ where $\beta$ is a tunable parameter. 
%Higher values of $\beta$ encourage over-segmentation.
Figure~\ref{fig:variation-of-information} shows our results for variables $\beta \in [0.5, 0.99]$. 
For our multicut analysis we use $\beta = 0.95$ (Sec.~\ref{sec:optimization}).

\subsection{Error Metrics}
\label{sec:variation-of-information}
We evaluate the performance of the different methods using the split variation of information (VI)~\cite{meila2003comparing}.
Given a ground truth labeling $GT$ and our automatically reconstructed segmentation $SG$, over- and under-segmentation are quantified by the conditional entropies $H(GT | SG)$ and $H(SG | GT)$, respectively. 
Since we are measuring the entropy between two clusterings, lower VI scores are better.
The sum of these conditional entropies gives the total variation of information.
